Supporting Information : The importance of a complete statistical description of dependence between variables for ecology and related fields

### 2018-07-11 SupportingInformation.Rmd
adding code for ceder creek data

@@

>>>>

## Ceder-creek data for e120 \label{ceder-creek_data}

```{r read_ceder_creek_data, echo=F, results="hide"}
set.seed(seed)
#-------------------------------------------------
# This function takes 
# Input :
#       db : a dataframe : smaller subset of ple_120 data to calculate avg. biomass for each plot
#       dp : a dataframe : smaller subset of pce_120 data to calculate avg. shannon's H for those plots
#       year : the year for which you want to calculate biomass and shannon's index data
#       rawplot : logical : T for rawdata plot, F for copula plot
#       ploton : logical for optional plotting

# Output :
#       a list of two data-frame:
#                   tab_dbp : a data-frame with 3 column : (plot no , avg.H, avg.Biomass(g/m2))
#                   cop_tab_dbp : a data-frame with 3 column : (plot no, pobs(avg.H), pobs(avg.Biomass(g/m2)))

cop_HB<-function(db,dp,year,rawplot,ploton){
  # db : biomass dataset for a specific year
  # dp : percent cover dataset for a specific year

  plots<-sort(intersect(db$Plot,dp$Plot)) # common plots for both datasets for a specific year
  db<-subset(db,Plot%in%plots)
  dp<-subset(dp,Plot%in%plots)

  tab_dbp<-data.frame(Plot=plots,avg.H=NA,avg.Biomass=NA)
  for(i in 1:length(plots)){
    # calculate biomass for each plot (averaged over all strips for that plot)
    x<-subset(db,Plot==plots[i])
    tab_dbp$avg.Biomass[i]<-mean(x$Biomass)

    # calculate shannon's index H for each plot (averaged over all Quadrates for that plot)
    x<-subset(dp,Plot==plots[i])
    uniq_sp<-sort(as.character(unique(x$Species)))  # These are the species in a particular plot
    Q<-as.character(unique(x$Quadrat))

    tab_each_sp<-data.frame(sp=uniq_sp,avg_cov=0,rel_avg_cov=0)

    for(sp in 1:length(uniq_sp)){
      my_sp<-uniq_sp[sp]
      tab_temp<-data.frame(Q=Q,abs_cov=0)
      ind<-which(x$Species==my_sp)
      li<-length(ind)
      tab_temp$abs_cov[1:li]<-x$Abscover[ind]
      tab_each_sp$avg_cov[[sp]]<-mean(tab_temp$abs_cov) # avg. over 4Quadrates for a sp.
    }

    tab_each_sp$rel_avg_cov<-tab_each_sp$avg_cov/sum(tab_each_sp$avg_cov)
    tab_dbp$avg.H[i]<- -sum((tab_each_sp$rel_avg_cov)*log(tab_each_sp$rel_avg_cov))

  tab_dbp<-na.omit(tab_dbp)

  cop_tab_dbp<-data.frame(Plot=tab_dbp$Plot,avg.H=NA,avg.Biomass=NA)
  cop_tab_dbp$avg.H<-VineCopula::pobs(tab_dbp$avg.H)
  cop_tab_dbp$avg.Biomass<-VineCopula::pobs(tab_dbp$avg.Biomass)

  if(ploton==T){
    if(rawplot==T){
      plot(tab_dbp$avg.H,tab_dbp$avg.Biomass,xlab="avg.H",ylab="avg.Biomass",col=rgb(0,0,1,0.3),pch=19,cex.lab=1.5)
      mtext(paste0("Year=",year))
    }else{
      plot(cop_tab_dbp$avg.H,cop_tab_dbp$avg.Biomass,xlab="avg.H",ylab="avg.Biomass",col=rgb(1,0,0,0.3),pch=19,cex.lab=1.5)
      mtext(paste0("Year=",year))
    }
  }

  return(list(tab_dbp=tab_dbp,
         cop_tab_dbp=cop_tab_dbp))
}
#-----------------------------
r_ple<-read.delim("./Data/Ceder_creek_e120/edited_ple120.txt")
r_pce<-read.delim("./Data/Ceder_creek_e120/edited_pce120.txt")

y1<-unique(r_ple$Year)
y2<-unique(r_pce$Year)
yr<-sort(intersect(y1,y2))

a<-as.data.frame(table(sort(r_pce$Species)))
b<-as.character(a$Var1)
bad_sp<-c(b[51:53],b[156:158])

ind<-which(r_pce$Species%in%bad_sp)
r_pce_clean<-r_pce[-ind,]
#--------------------------------------------------------------------------------------------
pdf("./Results/Ceder_creek_results/raw_HB_all_yr.pdf",height = 6,width = 10)
op<-par(mfrow=c(2,3),mar=c(3,3,3,3), mgp=c(1.5,0.5,0))
for(i in 1:length(yr)){
  db<-subset(r_ple,Year==yr[i])
  dp<-subset(r_pce_clean,Year==yr[i])

  sr<-cop_HB(db=db,dp=dp,year=yr[i],rawplot=T,ploton = T)
}
par(op)
dev.off()
#----------------------------------------------------------------------------------------
cop_HB_all_yr<-vector("list",length(yr))
names(cop_HB_all_yr)<-yr

pdf("./Results/Ceder_creek_results/cop_HB_all_yr.pdf",height = 6,width = 10)
op<-par(mfrow=c(2,3),mar=c(3,3,3,3), mgp=c(1.5,0.5,0))
for(i in 1:length(yr)){
  db<-subset(r_ple,Year==yr[i])
  dp<-subset(r_pce_clean,Year==yr[i])

  s<-cop_HB(db=db,dp=dp,year=yr[i],rawplot=F,ploton = T)
  cop_HB_all_yr[[i]]<-s$cop_tab_dbp[,2:3]
}
par(op)
dev.off()

saveRDS(cop_HB_all_yr,"./Results/Ceder_creek_results/cop_HB_all_yr.RDS")
#---------------------------------------------------------------------------------------
cop_HB_all_yr<-readRDS("./Results/Ceder_creek_results/cop_HB_all_yr.RDS")
```

@@

```{r bivmodselect_cc, echo=F, cache=T, cache.extra=list(seed,cop_HB_all_yr,mtime("OurBiCopSelect.R"),mtime("MyBiCopGofTest.R"),mtime("preprocessors.R"))}
source("OurBiCopSelect.R")
set.seed(seed)

BivMS_res_cc<-vector("list",length(cop_HB_all_yr))
names(BivMS_res_cc)<-names(cop_HB_all_yr)

for(i in 1:length(BivMS_res_cc)){
  BivMS_res_cc[[i]]<-OurBiCopSelect(u1=cop_HB_all_yr[[i]]$avg.H,u2=cop_HB_all_yr[[i]]$avg.Biomass,
                                    families=c(1,3:10,13:14,16:20),
                                    level=0.05,AICBIC="AIC",
                                    numBSsmall=100,pthresh=0.2,numBSlarge=1000,gofnormal=F,status=F)
}
saveRDS(BivMS_res_cc,file="./Results/Ceder_creek_results/BivMS_res_cc.RDS")
```

```{r stat_cc_graphic_approach, echo=F, results="hide", cache=T, cache.extra=list(seed,cop_HB_all_yr,mtime("bivfunctionplot.R"),mtime("CopulaFunctions_flexible.R"),mtime("copsurrog2d.R"))}
source("bivfunctionplot.R")
set.seed(seed)

stat_cc_ga<-vector("list",length(cop_HB_all_yr))
names(stat_cc_ga)<-names(cop_HB_all_yr)

for(i in 1:length(stat_cc_ga)){
  temp<-bivfunctionplot(v=cop_HB_all_yr[[i]],
                             resloc="./Results/Ceder_creek_results/",
                             nametag=paste0(names(cop_HB_all_yr)[i],"cc_numbin_10",sep=""),
                             numbin = 10)
  stat_cc_ga[[i]]<-temp
}

saveRDS(stat_cc_ga,"./Results/Ceder_creek_results/stat_cc_ga.RDS")
```
